Palomar 5 Gaps

### 2024-10-02 paper/main.tex
reducing the results a lot

    For each completed simulation, we follow the scheme laid out in the methods. I.e. we simulate the creation of the Palomar 5 stream for 50 different samplings of the initial conditions, with two different cases. The \textit{Full} simulation that includes the influence of all globualr clusters on the star particles representing Palomar 5 and its stream, as well as the \textit{vanilla} simulations in which the star-particles feel only the galaxy and Palomar 5.

    This comparative analysis is shown in Fig.~\ref{fig:profiles}. We visually compare the 2D density map in tail coordinates as well as their marginalized 1D density profiles along the length of Palomar 5's orbit. As described in section~XXX, we locate regions on the stream where the full simulations are significantly less dense than the vanilla simulations. We find that many streams as visible by eye. However, some subtle under densities only became apparent when comparing the 1D density profiles. All simulations and labeled gaps are presented in the Appendix~\ref{appendix:gallery_of_gaps}.

    Subsequently, we followed the analysis presented in section~\ref{sec:Perturber_Identification} to identify which globualr clusters were responsible for the gaps. This method used the orbit of Palomar 5 as a proxy for the stream. The gravitational force from all other globular clusters as computed at segments of the orbit about the position of Palomar 5 for the entire simulation. The top 5 strongest flybys were recorded to identify which cluster was responsible. This is shown in Fig.~\ref{fig:force-on-orbit}, where the top panel shows the force from the globular clusters on the orbit, while the bottom panel shows the density of the stream. A density threshold was imparted to quantify the length of the stream.  The location and time of impact was cross referenced to the location of the gaps to identify which cluster was responsible.

    For some cases, we performed a double check by launching extra simulations only including one suspect at a time to confirm that this suspect indeed caused a gap in question, an example is shown in Fig.~\ref{fig:decomposition}. Note that the gap from NGC~7078 was \textit{hit twice}.

@@

  \section{Gallery of Gaps} \label{appendix:gallery_of_gaps}

>>>>

    We apply the gap detection methods described in Appendix.~\ref{sec:gap_detection} and the perturber identification methods from Appendix.~\ref{sec:Perturber_Identification}. We present the results from all the simulations in Appendix.~\ref{sec:gallery_of_gaps}. Since we identify which perturber is responsible for a given gap, we launch the more simulations in which only one globular cluster at a time is included to isolate specific gaps. We present this in Fig.~\ref{fig:decomposition}.

@@

  \section{Gallery of Gaps} \label{sec:gallery_of_gaps}
